HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

The experiment seeks to address two questions:

\begin{compactitem}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{compactitem}

\subsection{UCCA Annotation}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists and one linguist.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair\oa{I think we should probably
  say how many in each.}.

These translation systems were used to translate texts derived from both NHS 24\footnote{\url{http://www.nhs24.com/}} and Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages. The first organisation is a public body providing healthcare and health-service related information in Scotland, whereas the second is an international NGO which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' which is part of the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.\bh{How much more do we need? Perhaps in the intro we could justify our focus on public health text
(accuracy!). The test corpora should have a public URL by the time we submit, although of course the source texts were 
already public anyway, and Lexi did some selection of examples for use in this expt. -- do we have to explain this?}

@@

>>>>

The experiment seeks to address two questions:
\begin{inparaenum}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{inparaenum}

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...

These translation systems were used to translate texts derived from both NHS 24\footnote{\url{http://www.nhs24.com/}} and Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages. The first organisation is a public body providing healthcare and health-service related information in Scotland, whereas the second is an international NGO which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' which is part of the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.

%\bh{How much more do we need? Perhaps in the intro we could justify our focus on public health text
%(accuracy!). The test corpora should have a public URL by the time we submit, although of course the source texts were 
%already public anyway, and Lexi did some selection of examples for use in this expt. -- do we have to explain this?}
% ... todo for the camera ready, if we get through

@@

Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists and one linguist.
